---
title: "Where Are Bees Headed?"
author: "Tate Reynolds and Thatcher Geary"
date: "4/19/2022"
output: ioslides_presentation
---

```{r data setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyUSDA)
library(tmap)
key <- 'B7A59EDE-41E6-31AC-8492-E88C629693FA'
tidyUSDA::allProgram %>% head()
honey.prod.2021 <- tidyUSDA::getQuickstat(
  sector='ANIMALS & PRODUCTS',
  group=NULL,
  commodity='HONEY',
  category=NULL,
  domain='TOTAL',
  county=NULL,
  key = key,
  program = 'SURVEY',
  data_item = 'HONEY - PRODUCTION, MEASURED IN LB / COLONY',
  geographic_level = 'STATE',
  year = '2021',
  state = NULL,
  geometry = TRUE,
  lower48 = FALSE, 
  weighted_by_area = T
)

honey.prod.2019 <- tidyUSDA::getQuickstat(
  sector='ANIMALS & PRODUCTS',
  group=NULL,
  commodity='HONEY',
  category=NULL,
  domain='TOTAL',
  county=NULL,
  key = key,
  program = 'SURVEY',
  data_item = 'HONEY - PRODUCTION, MEASURED IN LB / COLONY',
  geographic_level = 'STATE',
  year = '2019',
  state = NULL,
  geometry = TRUE,
  lower48 = FALSE, 
  weighted_by_area = T
)

honey.prod.2012 <- tidyUSDA::getQuickstat(
  sector='ANIMALS & PRODUCTS',
  group=NULL,
  commodity='HONEY',
  category=NULL,
  domain='TOTAL',
  county=NULL,
  key = key,
  program = 'SURVEY',
  data_item = 'HONEY - PRODUCTION, MEASURED IN LB / COLONY',
  geographic_level = 'STATE',
  year = '2012',
  state = NULL,
  geometry = TRUE,
  lower48 = FALSE, 
  weighted_by_area = T
)

honey.prod.2010 <- tidyUSDA::getQuickstat(
  sector='ANIMALS & PRODUCTS',
  group=NULL,
  commodity='HONEY',
  category=NULL,
  domain='TOTAL',
  county=NULL,
  key = key,
  program = 'SURVEY',
  data_item = 'HONEY - PRODUCTION, MEASURED IN LB / COLONY',
  geographic_level = 'STATE',
  year = '2010',
  state = NULL,
  geometry = TRUE,
  lower48 = FALSE, 
  weighted_by_area = T
)

honey.prod.2008 <- tidyUSDA::getQuickstat(
  sector='ANIMALS & PRODUCTS',
  group=NULL,
  commodity='HONEY',
  category=NULL,
  domain='TOTAL',
  county=NULL,
  key = key,
  program = 'SURVEY',
  data_item = 'HONEY - PRODUCTION, MEASURED IN LB / COLONY',
  geographic_level = 'STATE',
  year = '2008',
  state = NULL,
  geometry = TRUE,
  lower48 = FALSE, 
  weighted_by_area = T
)

honey.prod.2006 <- tidyUSDA::getQuickstat(
  sector='ANIMALS & PRODUCTS',
  group=NULL,
  commodity='HONEY',
  category=NULL,
  domain='TOTAL',
  county=NULL,
  key = key,
  program = 'SURVEY',
  data_item = 'HONEY - PRODUCTION, MEASURED IN LB / COLONY',
  geographic_level = 'STATE',
  year = '2006',
  state = NULL,
  geometry = TRUE,
  lower48 = FALSE, 
  weighted_by_area = T
)

honey.prod.2004 <- tidyUSDA::getQuickstat(
  sector='ANIMALS & PRODUCTS',
  group=NULL,
  commodity='HONEY',
  category=NULL,
  domain='TOTAL',
  county=NULL,
  key = key,
  program = 'SURVEY',
  data_item = 'HONEY - PRODUCTION, MEASURED IN LB / COLONY',
  geographic_level = 'STATE',
  year = '2004',
  state = NULL,
  geometry = TRUE,
  lower48 = FALSE, 
  weighted_by_area = T
)

honey.prod.2002 <- tidyUSDA::getQuickstat(
  sector='ANIMALS & PRODUCTS',
  group=NULL,
  commodity='HONEY',
  category=NULL,
  domain='TOTAL',
  county=NULL,
  key = key,
  program = 'SURVEY',
  data_item = 'HONEY - PRODUCTION, MEASURED IN LB / COLONY',
  geographic_level = 'STATE',
  year = '2002',
  state = NULL,
  geometry = TRUE,
  lower48 = FALSE, 
  weighted_by_area = T
)

honey.prod.2000 <- tidyUSDA::getQuickstat(
  sector='ANIMALS & PRODUCTS',
  group=NULL,
  commodity='HONEY',
  category=NULL,
  domain='TOTAL',
  county=NULL,
  key = key,
  program = 'SURVEY',
  data_item = 'HONEY - PRODUCTION, MEASURED IN LB / COLONY',
  geographic_level = 'STATE',
  year = '2000',
  state = NULL,
  geometry = TRUE,
  lower48 = FALSE, 
  weighted_by_area = T
)

honey.prod.1998 <- tidyUSDA::getQuickstat(
  sector='ANIMALS & PRODUCTS',
  group=NULL,
  commodity='HONEY',
  category=NULL,
  domain='TOTAL',
  county=NULL,
  key = key,
  program = 'SURVEY',
  data_item = 'HONEY - PRODUCTION, MEASURED IN LB / COLONY',
  geographic_level = 'STATE',
  year = '1998',
  state = NULL,
  geometry = TRUE,
  lower48 = FALSE, 
  weighted_by_area = T
)
hist(honey.prod.1998$Value)
tmap
tidyUSDA::plotUSDA(df=honey.prod.2021, fill_by = 'value_per_sq_mile')
tidyUSDA::plotUSDA(df=honey.prod.2019, fill_by = 'value_per_sq_mile')
all_data_2002 <- read.csv('data/Hone-02-28-2002/hony_all.csv', header=T)
all_data_2003 <- read.csv('data/Hone-02-28-2003/hony_all.csv', header=T)
all_data_2004 <- read.csv('data/Hone-02-27-2004/hony_all.csv', header=T)
all_data_2005 <- read.csv('data/Hone-02-28-2005/hony_all.csv', header=T)
all_data_2006 <- read.csv('data/Hone-02-28-2006/hony_all.csv', header=T)
all_data_2007 <- read.csv('data/Hone-02-28-2007/hony_all.csv', header=T)
all_data_2008 <- read.csv('data/Hone-02-29-2008/hony_all.csv', header=T)
all_data_2009 <- read.csv('data/Hone-02-27-2009/hony_all.csv', header=T)
all_data_2010 <- read.csv('data/Hone-02-26-2010/hony_all.csv', header=T)
all_data_2011 <- read.csv('data/Hone-02-25-2011/honey_2011.csv')
all_data_2012 <- read.csv('data/Hone-03-30-2012/hony_all_tables.csv')
all_data_2013 <- read.csv('data/Hone-03-18-2013/hony_all_tables.csv')
all_data_2014 <- read.csv('data/Hone-03-21-2014/hony_all_tables.csv')
all_data_2015 <- read.csv('data/Hone-03-20-2015/hony_all_tables.csv')
all_data_2016 <- read.csv('data/Hone-03-22-2016/hony_all_tables.csv')
all_data_2017 <- read.csv('data/Hone-03-22-2017/hony_all_tables.csv')
all_data_2018 <- read.csv('data/Hone-03-14-2018/hony_all_tables.csv')
all_data_2019 <- read.csv('data/hony0519/hony_all_tables.csv')
all_data_2020 <- read.csv('data/hony0320/hony_all_tables.csv')
all_data_2021 <- read.csv('data/hony0321/hony_all_tables.csv')
all_data_2022 <- read.csv('data/hony0322/hony_all_tables.csv')
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

